Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-11-04 paper/paper.tex
Spellcheck

The processing code, the cyberlioz interface and an anonimized version of the  perceptual judgments gathered using this interface are available at the companion website: \url{https://github.com/mathieulagrange/lostanlen2020jasmp}.

>>>>

The processing code, the Cyberlioz interface and an anonymized version of the  perceptual judgments gathered using this interface are available at the companion website: \url{https://github.com/mathieulagrange/lostanlen2020jasmp}.
